\hypertarget{index_intro_sec}{}\section{1. 1. Introduction}\label{index_intro_sec}
The Stargate project aims to create a mechanical system allowing mobile robots to open doors. Current version \+: 1.\+3

\hypertarget{index_multi_row}{}
\tabulinesep=1mm
\begin{longtabu} spread 0pt [c]{*3{|X[-1]}|}
\caption{Versioning table }\label{index_multi_row}\\
\hline
\rowcolor{\tableheadbgcolor}{\bf Version }&{\bf Functions }&{\bf Missing }\\\cline{1-3}
\endfirsthead
\hline
\endfoot
\hline
\rowcolor{\tableheadbgcolor}{\bf Version }&{\bf Functions }&{\bf Missing }\\\cline{1-3}
\endhead
0.\+1 &\char`\"{}go\+To\+Handle\char`\"{} and \char`\"{}move\+Door\char`\"{} stages are implemented &action\+Lib, interactions with Goa\textquotesingle{}Uld \\\cline{1-3}
0.\+2 &Every stages implemented, launched from Goa\textquotesingle{}Uld &Communications with the visual tracking \\\cline{1-3}
{\bfseries 1.\+0} &{\bfseries Final version of marc\textquotesingle{}s code} &{\bfseries Adapt the code with J\+A\+C\+K\+S\+ON} \\\cline{1-3}
1.\+1 &First modifications of marc\textquotesingle{}s code &Modify the trajectory generator \\\cline{1-3}
1.\+2 &New trajectory generator &Make it work !! \\\cline{1-3}
1.\+3 &Code working + first version of the documentation &action\+Lib, interactions with Goa\textquotesingle{}Uld \\\cline{1-3}
\end{longtabu}
\hypertarget{index_navigation}{}\section{2. Principles of the Navigation code.}\label{index_navigation}
v1.\+3 \+: using the command \char`\"{}rosrun navigation cmd\+\_\+ouverture.\+py\char`\"{} launches the navigation code.

The file \hyperlink{cmd__ouverture_8py}{cmd\+\_\+ouverture.\+py} is the main file. It computes the desired trajectory based on the current {\itshape stage} and {\itshape step} using \hyperlink{classPointCreator}{Point\+Creator} and \hyperlink{classTrajFactory}{Traj\+Factory}.

It then launches the control law in control.\hypertarget{index_phases_and_steps}{}\section{3. Descriptions of the phases and steps that make up a door opening.}\label{index_phases_and_steps}
When trying to open a door by pulling it, here are the different stages that Goa Uld will launch. Each of them contains one or more steps. 